Main text : Effect of copula on extinction risk

### 2019-02-27 MainText.Rmd
adding figures...continued

>>>>

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_info} extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$ for local dispersion. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime in deterministic model analog.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure}

 <!--FIG : all nonlinear model results with d=0, extrisk vs. r-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=5 cm]{./Results/ricker_scl_1/ricker_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/hassell_scl_1/hassell_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf}\\
\caption{Extinction risk varies with bifurcation parameter $(r)$ for all nonlinear density-dependence models without dispersal, numsims=10000. \label{fig_extrisk_d0}}
\end{center}
\end{figure}
